API design for machine learning software: experiences from the scikit-learn project

### 2013-06-26 paper.tex
forgot "with"

In comparison to specialized languages for numeric and statistical programming
such as \textsc{matlab} and R \citep{r},
Python has the distinct advantage
that it is a \textit{general purpose} language,
while NumPy and SciPy extend it functionality
similar to that offered by \textsc{matlab} and R.
Python has strong language and standard library support for such tasks as
string/text processing, interprocess communication, networking
and many of the other tasks that machine learning programs
(whether academic or commercial) routinely need to perform.
However, \textsc{matlab} and R remain the preferred language of many
researchers. As such, much scientific software is still open-sourced primarily
in these two languages.

>>>>

In comparison to specialized languages for numeric and statistical programming
such as \textsc{matlab} and R \citep{r},
Python has the distinct advantage
that it is a \textit{general purpose} language,
while NumPy and SciPy extend it with functionality
similar to that offered by \textsc{matlab} and R.
Python has strong language and standard library support for such tasks as
string/text processing, interprocess communication, networking
and many of the other tasks that machine learning programs
(whether academic or commercial) routinely need to perform.
However, \textsc{matlab} and R remain the preferred language of many
researchers. As such, much scientific software is still open-sourced primarily
in these two languages.
